|

### 2023-02-07 paper_comparison/paper_comparison/paper_comparison.Rmd
update the conclusion

According to the data collected from the human subject experiment, residual plots rejected by visual tests are rarely not rejected by conventional tests, but departures of residuals that are of little practical sense to humans will often be alarmed by conventional tests, supporting the common guidance given by experts to utilize graphical representations of data in model diagnostics.

We have also found that residual-based conventional tests relying on a user-parameterized test formula, such as the RESET test, will suffer from a significant decrease in power for detecting certain residual departures intended to be tested but not covered by the test formula. This can not be avoided without prior knowledge of their functional forms, which is usually obtained by plotting the residuals. On the other hand, visual tests do not rely on such information and a collection of departures can be tested simultaneously.

Interestingly, the orientation of the visual pattern

fitted value distribution

orientation of heter shape

>>>>

According to the data collected from the human subject experiment, residual plots rejected by visual tests are rarely not rejected by conventional tests, but departures of residuals that are of little practical sense to humans are sometimes alarmed by conventional tests, supporting the common guidance given by experts to utilize graphical representations of data in model diagnostics. We have also found that residual-based conventional tests relying on a user-parameterized test formula, such as the RESET test, will suffer from a significant decrease in power for detecting certain residual departures intended to be tested but not covered by the test formula. This is difficult to be avoided without prior knowledge of their functional forms, which is usually obtained by plotting the residuals. On the other hand, visual tests do not rely on such information and a collection of departures can be tested simultaneously. Interestingly, subjects recruited for our experiment behaves a potential favour of the orientation of the residual departure patterns. They perform slightly better in identifying triangle residual patterns pointing to the left than to the right. Besides, it is found that fitted value distributions have a great impact on the power of both conventional and visual tests. Generally, fitted values followed an evenly distributed and symmetric distribution such as the uniform distribution is preferred. Depending on the type of the residual departures, discreteness may cause trouble to humans to identify the residual patterns, while conventional tests are not affected. Skewness on the other hand significantly decrease the power of both conventional and visual tests when testing heteroskedasticity. Although it is commonly assumed by analysts, a normal fitted value distribution may not be the optimal option when comes to regression diagnostics.
